|

### 2025-07-16 output/IMPS-2025-slideshow.qmd
Fix complete item representation plot

::: {.column .fragment}
```{r item-plot-out}
#| fig-cap:   Item representation in non-orthonormal test space
#| fig-align: center
plot_oblique +
  scale_color_manual(values = ITEMS_PALETTE, guide = NULL) +
  theme(axis.ticks = element_blank()) ## TODO: Tema ggplot
```
:::
:::::

>>>>

::: {.column .fragment}
```{r item-plot-out}
#| fig-cap:   Item representation in non-orthonormal test space
#| fig-align: center
transform_grid(
  ts_basis,
  x_limits   = c(-2, 3),
  y_limits   = c(-2, 2.8),
  break_step = 1
) +
  geom_segment(
    arrow     = arrow(angle = 20, length = unit(10, "points"), type = "closed"),
    linejoin  = "mitre",
    linewidth = VECTOR_WIDTH,
    data      = items_oblique |> arrange(desc(item)),
    mapping   = aes(
      origin_transf_1, origin_transf_2,
      xend  = end_transf_1, yend = end_transf_2,
      color = item, fill = item
    )
  ) +
  scale_color_manual(values = PALETTE, guide = NULL) +
  coord_fixed(expand = FALSE, clip = "on")
```
:::
:::::
